---
title: "An overview of the impacts of global warming on climate and ^[Code and data are available in this GitHub repository: git]"
date: "27 April 2022"
author: "Cheng Chen"
lang: "en"
output:
  pdf_document:
    toc: true
    toc_depth: 2
abstract: "The degree of regional climate change, particularly regional rainfall, is particularly relevant in agriculture. Sufficient  is beneficial to agricultural growth, while excessive or insufficient  has negative consequences for crops. Artificial crop water content intervention is essential at this time. In this paper, the yearly rainfall in England and Wales are collected and explored via multiple linear regression model and two sample t-test, then the variability of raindrop is investigated in order to give feasible suggestions to the algriculture.\\par\\textbf{Keywords:} Water, , regression analysis, ANOVA, multiple comparison link:https://github.com/ca99328/STA304_FinalPaper.git" 
bibliography: ref.bib
---


```{r message=FALSE, warning=FALSE, include=FALSE}
#Load packages
library(moments)
library(reshape2)
library(ggplot2)
library(dplyr)
library(gridExtra)

```


```{r message=FALSE, warning=FALSE, include=FALSE}
#Load in Dataset
rainfall = read.csv('data.csv')
for (i in 2:length(rainfall)) {
  print('Variable')
  print(mean(rainfall[[i]], na.rm=TRUE))
  print(median(rainfall[[i]], na.rm=TRUE))
  print(sd(rainfall[[i]], na.rm=TRUE))
  print(max(rainfall[[i]], na.rm=TRUE) - min(rainfall[[i]], na.rm=TRUE))
  print(IQR(rainfall[[i]], na.rm=TRUE))
  print(skewness(rainfall[[i]], na.rm=TRUE))
  print(kurtosis(rainfall[[i]], na.rm=TRUE))
}
# Correlation matrix Heatmap
cormat <- round(cor(rainfall),2)
melted_cormat <- melt(cormat)
ggplot(data = melted_cormat, aes(x=Var1, y=Var2, fill=value))  + 
  geom_tile() + xlab("") + ylab("") +
  theme(axis.text.x=element_text(angle=45, hjust=1))
# Scatterplot
mslp <- ggplot(rainfall, aes(mslp, rainfall)) + geom_smooth(method = "loess")
w <- ggplot(rainfall, aes(w, rainfall)) + geom_smooth(method = "loess")
s <- ggplot(rainfall, aes(s, rainfall)) + geom_smooth(method = "loess")
brestzon <- ggplot(rainfall, aes(brestzon, rainfall)) + geom_smooth(method = "loess")
kefzon <- ggplot(rainfall, aes(kefzon, rainfall)) + geom_smooth(method = "loess")
corunmer <- ggplot(rainfall, aes(corunmer, rainfall)) + geom_smooth(method = "loess")
naoi <- ggplot(rainfall, aes(naoi, rainfall)) + geom_smooth(method = "loess")
sstatlan <- ggplot(rainfall, aes(sstatlan, rainfall)) + geom_smooth(method = "loess")
sstengch <- ggplot(rainfall, aes(sstengch, rainfall)) + geom_smooth(method = "loess")
sstmed <- ggplot(rainfall, aes(sstmed, rainfall)) + geom_smooth(method = "loess")
grid.arrange(mslp, w, s, brestzon, kefzon, corunmer, naoi, sstatlan, sstengch, sstmed, ncol = 3, nrow = 4)
# Regression 
model = lm(data = rainfall, rainfall ~ mslp + brestzon + kefzon + sstatlan + sstengch)
summary(model)
# two-sample t-test
sample1 = rainfall$rainfall[1:24]
sample2 = rainfall$rainfall[25:50]
t.test(sample1, sample2, var.equal = FALSE)
```
\newpage

# Introduction

Climate change in  is the accumulation of liquid or frozen dihydrogen monoxide in the atmosphere that falls to the ground's surface. Because all plants require water for chemical activities such as photosynthesis, rainfall is critical to agriculture. Sufficient  is necessary for normal agricultural growth, but excessive or insufficient  has a detrimental effect on crops, even killing them. Understanding agricultural crop rainfall is crucial for designing cropping systems that are adaptable to climate change-induced pressures (@10). 

Scientists have demonstrated the enormous influence and interference that humans may have on the rainfall system. Rainwater harvesting agriculture is used to sustain agricultural output. The average annual rainfall (APP) information system, which was developed using optimised methods and raster rainfall spatial databases, is capable of quickly and accurately calculating the total quantities and spatial shifts of rainfall resources for almost any measurement in the study areas, which is useful for runoff simulation, engineering planning, strategy development, and decision making, as well as water management in rainwater harvesting agriculture (@11). 

The purpose of this study is to identify the elements that determine local rainfall in England and to understand how their variability is influenced. The data comes from the Met Office's Hadley Centre and covers the years 1951 to 1999. To aid in our understanding of the important elements affecting rainfall in England and Wales, we provide a few questions and begin by answering the following, which will provide more insights and possible summaries on rainfall. The following is the pertinent question:

\begin{itemize}
\item From the explanatory view, which are variables that highly relates to the  in England and wales?
\item From the statistical view, what variables significantly influences the quantity?
\item If we divide the yearly raindrop into two time interval (from 1951 to 1975 versus from 1876 to 1999), are the two time period average raindrops differ from each other signifiantly in statistics?
\end{itemize}

To answer the first question, we can use basic data analysis techniques to determine which variables have a linear relation with  by plotting the independent versus dependent variable rainfall. We can also use the Pearson correlation coefficient to determine which variables have a linear relationship with . The second task is to develop a multivariate linear regression model in order to identify statistically relevant variables. The third issue may be resolved by doing hypothesis testing and calculating the P-value on quantitative samples to see whether the sample means of the two time periods are substantially different. 

The textbfData portion of this article begins with basic statistics and figures that depict the overall distribution and other data about the original dataset. To address the above problems, many techniques are utilised, including a linear regression model and a t test for two observational series. The textbfMethodology section provides an overview and introduction to the methods used in our study. The textbfResult part contains the R output and the results generated by our statistical techniques, while the textbfDiscussion section will focus on the understanding of rainfall in England and Wales as a consequence of the methods' output, the methods' shortcomings, and prospective future works. The data set will be handled using R (@1) and a handful of tidyverse-related programmes inside R (@2). ggplot2 (@3), dplyr (@4), kableextra (@5), moment (@6), reshape2 (@7), and gridExtra (@8) are also used to create the majority of the figures and tables. Additionally, the knitr (@9) package was used to build this R markdown report.

\newpage

# Data
To begin, here is a fast EDA of the data and a short glimpse of the variable distributions.
```{r echo=FALSE, fig.height=4, message=FALSE, warning=FALSE}

ggplot(rainfall, aes(x=mslp))+
  geom_histogram(color="blue", fill="red")+
  theme_minimal()+
  labs(title = "Fig 0.1: Distributions of the variables")
```
It is evident that the majority of the data was Distributed from -250 to 500 mslp. 

```{r echo=FALSE, fig.height=4, message=FALSE, warning=FALSE}
ggplot(rainfall, aes(x=sstatlan))+
  geom_histogram(color="blue", fill="red")+
  theme_minimal()+
  labs(title = "Fig 0.2: Distributions of the variables")
```
From plot it is evident that the the sea-level temp is mostly 0 and evenly distribute on the x-axis. 
```{r include=FALSE}

rainfall = read.csv('data.csv')
for (i in 2:length(rainfall)) {
  print('Variable')
  print(mean(rainfall[[i]], na.rm=TRUE))
  print(median(rainfall[[i]], na.rm=TRUE))
  print(sd(rainfall[[i]], na.rm=TRUE))
  print(max(rainfall[[i]], na.rm=TRUE) - min(rainfall[[i]], na.rm=TRUE))
  print(IQR(rainfall[[i]], na.rm=TRUE))
  print(skewness(rainfall[[i]], na.rm=TRUE))
  print(kurtosis(rainfall[[i]], na.rm=TRUE))
}
```
The data originates from the Met Office's Hadley Centre and covers the years 1951 to 1999(@12 @13 @14 @15 @16). The table below contains a description of each variable. We begin by obtaining descriptive statistics on the data as a whole. Calculating the mean, median, quantile, kurtosis, and skewness of a sample is considered descriptive statistics. To assist readers in comprehending the factors associated with climate terminology, we subdivide the 10 independent variables into three groups: 

1. Pressure and wind factors (mean sea-level pressure, westerly and southerly wind forces, and the North Atlantic oscillation index) that can exert a major influence on the Earth's weather and climate. 

2. Components of the water vapour flow (zonal at $Brest1$, $Keflavik2$, and $La Coruna1$) that impact rainfall due to differing gas contents. 

3. Sea-surface temperatures (eastern North Atlantic, $English Channel1$, and $Mediterranean Sea2$), which are related to the quantity of water vapour in the atmosphere above the seas and the danger of .

| Variable | Description                          | Mean   | Median | SD    | Range | IQR   | Skew  | Kurt |
|----------|--------------------------------------|--------|--------|-------|-------|-------|-------|------|
|  | Winter rainfall                 | 253.6  | 252.7  | 72.1  | 332   | 85.7  | 0.30  | 2.92 |
| mslp     | Mean sea-level pressure              | -12.35 | -53.2  | 382.8 | 1765  | 529.3 | 0.18  | 2.87 |
| w        | The westerly wind component    | 18.61  | 3.57   | 166.3 | 704.9 | 237.1 | -0.06 | 2.42 |
| s        | The southerly wind component   | -7.12  | 14.63  | 100.3 | 452.9 | 125.1 | -0.31 | 2.75 |
| brestzon | The zonal water vapour $flux^1$          | 0.04   | 0.22   | 0.80  | 3.74  | 1.19  | -0.33 | 2.71 |
| kefzon   | The zonal water vapour $flux^2$           | 0.06   | -0.04  | 0.56  | 2.61  | 0.73  | 0.41  | 2.76 |
| corunmer | The meridional water vapour $flux^1$   | 0.13   | 0.14   | 1.88  | 9.65  | 2.15  | -0.61 | 3.86 |
| naoi     | The North Atlantic oscillation index | 0.35   | 0.14   | 1.35  | 5.46  | 1.66  | -0.03 | 2.50 |
| sstatlan | Sea-surface temperature              | 0.17   | 0.10   | 0.41  | 1.81  | 0.61  | 0.05  | 2.49 |
| sstengch | Sea Surface Temperature $anomalies^1$  | 0.06   | 0.08   | 0.49  | 2.77  | 0.59  | -0.30 | 4.41 |
| sstmed   | Sea Surface Temperature $anomalies^2$  | 0.11   | -0.10  | 0.84  | 4.56  | 1.20  | 0.30  | 3.68 |

The correlation matrix heatmap enables us to easily visualise the relationship between dependent and independent variables inside a dataset. Correlation coefficients are displayed in the heatmap below; the deeper the blue colour of the bar, the closer the coefficient is to 1, and the lighter the blue colour of the bar, the closer the coefficient is to -1.

```{r echo=FALSE}
# Correlation matrix heatmap
cormat <- round(cor(rainfall),2)
melted_cormat <- melt(cormat)
ggplot(data = melted_cormat, aes(x=Var1, y=Var2, fill=value))  + 
  geom_tile() + xlab("") + ylab("") +
  theme(axis.text.x=element_text(angle=45, hjust=1))+
  labs(title = "Fig.1: Correlation matrix heatmap")
```


For a basic linear regression model, the square of the Pearson correlation coefficient is comparable to $R2$. The formula for the Pearson correlation coefficient is as follows: $$r_{XY}=\frac{Cov\left(X,Y\right)}{\sqrt{Var\left(X\right)\ast Var\left(Y\right)}}$$  The independent variable's and dependent variable's absolute values being closer to one demonstrates the importance of including the independent variable while developing the regression model. In the majority of cases, the absolute value of $rho$ indicates that a linear relationship exists between two variables. mslp, brestzon, kefzon, sstatlan, and sstengch all satisfy this requirement, as seen by the heatmap and R calculation results. 

The Pearson correlation coefficient establishes an initial relationship between the variables; the next step is to examine the particular scatter plot to see whether the linear relationship exists.

```{r echo=FALSE, message=FALSE, warning=FALSE}

mslp <- ggplot(rainfall, aes(mslp, rainfall)) + geom_smooth(method = "loess")
w <- ggplot(rainfall, aes(w, rainfall)) + geom_smooth(method = "loess")
s <- ggplot(rainfall, aes(s, rainfall)) + geom_smooth(method = "loess")
brestzon <- ggplot(rainfall, aes(brestzon, rainfall)) + geom_smooth(method = "loess")
kefzon <- ggplot(rainfall, aes(kefzon, rainfall)) + geom_smooth(method = "loess")
corunmer <- ggplot(rainfall, aes(corunmer, rainfall)) + geom_smooth(method = "loess")
naoi <- ggplot(rainfall, aes(naoi, rainfall)) + geom_smooth(method = "loess")
sstatlan <- ggplot(rainfall, aes(sstatlan, rainfall)) + geom_smooth(method = "loess")
sstengch <- ggplot(rainfall, aes(sstengch, rainfall)) + geom_smooth(method = "loess")
sstmed <- ggplot(rainfall, aes(sstmed, rainfall)) + geom_smooth(method = "loess")
grid.arrange(mslp, w, s, brestzon, kefzon, corunmer, naoi, sstatlan, sstengch, sstmed, ncol = 3, nrow = 4)
```

We now present a scatter plot of rainfall vs. the other independent variable. Mslp, brestzon, kefzon, sstengch, and sstmed all appear to have a linear relationship with the rainfall variable in the plot. This matches the Pearson correlation coefficient value. As a result, these five variables are included in our regression model.

# Methodology

The purpose of this study is to identify the elements that determine local rainfall in England and to understand how their variability is influenced. By addressing the three concerns raised above, we acquire a better understanding of and insight into the entire dataset. To answer the first question: textbfFrom the explanatory description analysis, which factors are strongly associated to rainfall in England and Wales?, we utilise the Pearson correlation coefficient and present the analysis results in the textbfData section. For the second question: textbfWhat factors have a substantial effect on rainfall, based on the statistical methodologies used?, we will use the multiple linear regression model. The initial model attempts to construct a regression relationship using rainfall as the response variable and five variables (mslp, brestzon, kefzon, sstengch, and sstmed) as predictors. The following is the regression equation: $$rainfall = \beta_0 + \beta_1 mslp + \beta_2 brestzon + \beta_3 kefzon + \beta_4 sstengch + \beta_5 sstmed + \epsilon$$


By examining the sign and magnitude of the regression coefficient, we may deduce the relationships between the five critical variables and the rainfall variable. The last query: \textbf If we divide the annual  into two time intervals (from 1951 to 1975 and from 1876 to 1999), do the two time periods' average raindrops differ significantly in statistics? is connected to the total fluctuation in rainfall in England and Wales. We are interested in resolving this question because it may reveal whether certain immediate tactics are essential to employ if rainfall changes significantly. Two sample t tests are used to address this subject. We concentrate on the average rainfall level while also taking into account the variability within each time interval. The hypothesis test technique is applied, and the statistic (if the null hypothesis is true, it follows the student t distribution) is as follows: $$\frac{\overline{X}_1-\overline{X}_2}{\sqrt{\frac{s_1^2}{n_1}+\frac{s_2^2}{n_2}}},\ df = \frac{(\frac{s_1^2}{n_1}+\frac{s_2^2}{n_2})^2}{\frac{(s_1^2/n1)^2}{n_1-1}+\frac{(s_2^2/n2)^2}{n_2-1}}$$
By looking at the P-value of the hypothesis test, we are able to answer question 3.

The other two critical ways I will use to analyse the data are to examine the P-value and to run a t-test on the statistical model that was constructed.

## P-value:
The p-value is a numerical value calculated during a statistical hypothesis test that indicates the probability of discovering a set of observations. It is used in hypothesis testing to assist in determining whether or not to reject the null hypothesis. A smaller p-value indicates a greater likelihood that the null hypothesis will be rejected. Typically, a P-value is considered low when it is less than 0.05, indicating that there is some evidence to reject the null hypothesis.

## T-test:
A t-test is an inferential statistic that is used to determine whether there is a statistically significant difference in the means of two groups that are somehow related. A t-test is a hypothesis testing tool that may be used to evaluate a population-based assumption.

# Results

## Factors that effect 

In the Data section, we observe that the variables with a Pearson correlation coefficient of greater than 0.3 or less than -0.3 with rainfall are mslp, brestzon, kefzon, sstatlan, and sstengch. Additionally, the smooth line fitted by the built-in R function demonstrates the same relationship between these five factors and rainfall. We can observe that pressure and wind force (ocean sea-level pressure over the British Isles), water vap-flux components (Brest and Keflavik), and sea-surface temperatures (eastern and English) are all connected to rainfall in England and Wales.

## statistically signficant impact factors

According to the data section, mslp, brestzon, kefzon, sstengch, and sstmed appear to have a linear relationship with the rainfall variable as determined by the scatter plot and Pearson correlation coefficient, and thus will be used in the multiple linear regression model as five of the ten variables. The equation for the regression model is as follows: $$Y = \beta_0 -0.128 X_1 + 18.422 X_2 + 1.073 X_3 -23.053 X_4 + 9.638 X_5 + \epsilon$$
The vairable and its representation is:
\begin{itemize}
\item $Y$: rainfall
\item $X_1$: mean sea-level pressure above British Islesl
\item $X_2$: zonal water vap-flux anomaly at Brest
\item $X_3$: zonal water vap-flux anomaly at Keflavik
\item $X_4$: above sea temperature at eastern Atlantic
\item $X_5$: above sea temperature at English
\end{itemize}

The regression output is given below:

| Variable | Description                          |  Estimate | Std. Error | t value    | P-value |
|----------|--------------------------------------|--------|--------|-------|-------|
| mslp     | Mean sea-level pressure              | -0.12783 | 0.02785  | -4.590 | 3.83e-05  |
| brestzon | The zonal water vapour $flux^1$          | 18.42217   | 9.6272   | 1.914  | 0.0623  |
| kefzon   | The zonal water vapour $flux^2$           | 1.07303   | 15.02184 | 0.071  | 0.9434  | 
| sstatlan | Sea-surface temperature              | -23.05318   | 13.14552   | -1.754  | 0.866  |
| sstengch | Sea Surface Temperature $anomalies^1$  | 9.63816   | 10.86659   | 0.887  | 0.38  |
```{r include=FALSE, paged.print=FALSE}
model = lm(data = rainfall, rainfall ~ mslp + brestzon + kefzon + sstatlan + sstengch)

summary(model)
```
The impact for five of the variables:
\begin{itemize}
\item If the mean sea-level pressure is increased by 1 millibar, the average rainfall should drop by 0.128 mm. 
\item If the zonal water vapour flow anomaly at Brest increases by 1 kilogramme per metre per millibar per second, the average rainfall should rise by 18.422 millimetres. 
\item If the zonal water vapour flux anomaly in Keflavik increases by 1 kilogramme per metre per millibar per second, the average rainfall should rise by 1.073 millimetres. 
\item If the temperature above sea level increases by 1 degree Celsius in the eastern hemisphere, the average rainfall is anticipated to drop by 23.053 mm. 
\item If the temperature above sea level in the English Channel increases by 1 degree Celsius, the average rainfall will rise by 9.638 mm.
\end{itemize}

The variables mslp, brestzon, and sstatlan are significant at the 90% confidence level (P-value less than 0.1). The regression model's $R^2$ value is 0.80, indicating that the multiple regression model accounts for 80% of the variation in raindrops. In conclusion, when considering the factors that influence rainfall in England and Wales, we should observe that the mean sea-level pressure over the British Isles has a significant effect on rainfall, the zonal water vap-flux anomaly at Brest has a significant effect on rainfall, and the sea-surface temperatures in the eastern North Atlantic have a statistically significant effect on rainfall. 

Additionally, the mean sea-level pressure and sea-surface temperatures over the British Isles have a positive effect, whereas the zonal water vap-flux at Brest has a negative effect. Thus, the zonal water vap-flux at Brest and the sea-surface temperatures over the British Isles have a much greater effect than the mean sea-level pressure (18.42 versus -0.13 and -23.05 versus -0.13).

```{r echo=FALSE}
par(mfrow = c(2,2))
plot(model)
```
The top four charts indicate the regression model's quality of fit. The residuals vs fitted plot indicates that the residuals are generally zero mean but are not evenly distributed, indicating that the variable is not constant. The regular Q-Q plot indicates that the regreesion model is normal, and there do not appear to be any high leverage spots.

##  amount varies over time

```{r message=FALSE, warning=FALSE, include=FALSE}
# two sample t test
sample1 = rainfall$rainfall[1:24]
sample2 = rainfall$rainfall[25:50]
t.test(sample1, sample2, var.equal = FALSE)
```
If we divide the annual  into two time intervals (between 1951 and 1975 and between 1876 and 1999), do the two time periods' average raindrops differ significantly in terms of statistics? To address the question, the two sample t test (independent and unequal variance assumptions required) can be used. The test statistic is -0.996, which numerically indicates that the average rainfall falls with time due to the negative sign. However, when the variance between the two samples is included, the P-value is 0.32, indicating that the negative sign (reduction in average rainfall in England and Wales) is consistent with expectation, and the drop is due to the modest variation between the two samples. Thus, statistically, we conclude that there is no change in the mean number of raindrops between the two time periods (from 1951 to 1975 versus from 1976 to 1999).


# Discussion

Two subsections comprise the discussion section. The first chapter discusses the interpretation of the results for the three research topics and the knowledge of rainfall in England and Wales; the second subsection discusses the methodology's inherent flaws and potential future adjustment efforts.

## Summary and analysis of strength and weakness

As a consequence of the statistical study, we can observe that pressure and wind force (ocean sea-level pressure across the British Isles), water vap-flux components (Brest and Keflavik), and above sea temperatures (eastern and English) are all associated with rainfall in England and Wales. 

Additionally, the regression model result indicates that the mean sea-level pressure over the British Isles has a significant effect on the raindrops; if the mean sea-level pressure is increased by 1 millibar, the average rainfall is expected to decrease by 0.128 millimetres; and the zonal water vap-flux anomaly at Brest has a significant effect on the raindrops; if the zonal water vap-flux anomaly at Brest is increased by 1 kilogrammes per 

By examining the three major variables, we can find that the zonal water vap-flux anomaly at Brest and the above-sea temperatures throughout the British Isles have a significantly greater effect than the mean sea-level pressure (18.42 versus -0.13 and -23.05 versus -0.13). 

To provide more accurate feedback to agriculture in England and Wales, the fundamental mean sea-level pressure must be monitored. Additionally, the zonal water vap-flux anomaly at Brest is related with rainfall in England but not with the zonal water vap-flux anomaly in Iceland (which is closer to England), which might be explained by their shared latitude. As a result, the idea is to monitor the zonal water vap-flux anomaly in geographical locations with a similar latitude to England and Wales. Sea-surface temperatures over the British Isles must be monitored since they are closer to the mainland of England and are thus more likely to impact neighbouring rainfall. When we look at the total variance in rainfall in England and Wales, we notice that there is no substantial difference between the two time periods, indicating that no immediate measures are required because rainfall does not fluctuate drastically.

## Future Works

We find certain inherent flaws in the technique and results sections. The regression diagnostics indicate that the residuals lack constant variance, implying that additional transformations, such as box-cox transformations, are required to resolve the issues. Additionally, the regression model considers only five variables. In the regression model, $R^2 = 0.7997$, indicating that the distance can account for 79.97 percent of the variation in damage percent. If we can gather additional critical data (i.e., the local in-land temperature) and account for other variables, we can increase the $R^2$. However, because the increased $R^2$ may be due to overfitting, future study should include both increased variate collection and variable selection and dimension reduction procedures.

\newpage


# Appendix
## Data sheet:

1. *For what purpose was the dataset created? Was there a specific task in mind? Was there a specific gap that needed to be filled? Please provide a description.*
    -Initially, the information was generated for agricultural purposes. Its purpose is to keep track of the rainfall over the United Kingdom.
2. *Who created the dataset (for example, which team, research group) and on behalf of which entity (for example, company, institution, organization)?*
    - This dataset was created by a group of scientist: Alexander and Jones (2001) Jones and Conway (1997) Gregory J. M. and Wigley(1991) T. M. L. Wigley and Jones (1987) J. M. L. Wigley T. M. L. and Jones (1984)
3. *Who funded the creation of the dataset? If there is an associated grant, please provide the name of the grantor and the grant name and number.*
    - N/A
4. *Any other comments?*
    - N/A

**Composition**

1. *What do the instances that comprise the dataset represent (for example, documents, photos, people, countries)? Are there multiple types of instances (for example, movies, users, and ratings; people and interactions between them; nodes and edges)? Please provide a description.*
	- This data collection was collected exclusively in the United Kingdom and used as national data. and is distinguished by the many measurements required by the scientific community. They are data on sea level, water vapour, and wind.
2. *How many instances are there in total (of each type, if appropriate)?*
	- sea-level data:4
	- water vapour: 4
	_ wind data: 2
3. *Does the dataset contain all possible instances or is it a sample (not necessarily random) of instances from a larger set? If the dataset is a sample, then what is the larger set? Is the sample representative of the larger set (for example, geographic coverage)? If so, please describe how this representativeness was validated/verified. If it is not representative of the larger set, please describe why not (for example, to cover a more diverse range of instances, because instances were withheld or unavailable).*
	-  It is very hard to include all elements while doing a study of nature; moreover, this is constrained by the technology available in the 1990s.
4. *What data does each instance consist of? "Raw" data (for example, unprocessed text or images) or features? In either case, please provide a description.*
	- all data are numeric.
5. *Is there a label or target associated with each instance? If so, please provide a description.*
	- There are no associated label or target to each instance.
6. *Is any information missing from individual instances? If so, please provide a description, explaining why this information is missing (for example, because it was unavailable). This does not include intentionally removed information, but might include, for example, redacted text.*
	- There are a few instances of missing data across the data collection, however they are minor in comparison to the bulk of the data.
7. *Are relationships between individual instances made explicit (for example, users' movie ratings, social network links)? If so, please describe how these relationships are made explicit.*
	- There are no particular relationships between the instances.
8. *Are there recommended data splits (for example, training, development/validation, testing)? If so, please provide a description of these splits, explaining the rationale behind them.*
	- There are no recommended data splits.
9. *Are there any errors, sources of noise, or redundancies in the dataset? If so, please provide a description.*
	- There are no errors, noise, or redundancies in thea dataset.
10. *Is the dataset self-contained, or does it link to or otherwise rely on external resources (for example, websites, tweets, other datasets)? If it links to or relies on external resources, a) are there guarantees that they will exist, and remain constant, over time; b) are there official archival versions of the complete dataset (that is, including the external resources as they existed at the time the dataset was created); c) are there any restrictions (for example, licenses, fees) associated with any of the external resources that might apply to a dataset consumer? Please provide descriptions of all external resources and any restrictions associated with them, as well as links or other access points, as appropriate.*
	- This dataset is self-contained. 
11. *Does the dataset contain data that might be considered confidential (for example, data that is protected by legal privilege or by doctor-patient confidentiality, data that includes the content of individuals' non-public communications)? If so, please provide a description.*
	- There are no data contained in the data set that will be considered condidential.
12. *Does the dataset contain data that, if viewed directly, might be offensive, insulting, threatening, or might otherwise cause anxiety? If so, please describe why.*
	- This data did not include any information that will be considered offensive. 
13. *Does the dataset identify any sub-populations (for example, by age, gender)? If so, please describe how these subpopulations are identified and provide a description of their respective distributions within the dataset.*
	- The dataset studies the information of nature, and should not include any sub-population. 
14. *Is it possible to identify individuals (that is, one or more natural persons), either directly or indirectly (that is, in combination with other data) from the dataset? If so, please describe how.*
	- Due to the nature of this data-set, it is not possible to identify any individuals in this data-set. 
15. *Does the dataset contain data that might be considered sensitive in any way (for example, data that reveals race or ethnic origins, sexual orientations, religious beliefs, political opinions or union memberships, or locations; financial or health data; biometric or genetic data; forms of government identification, such as social security numbers; criminal history)? If so, please provide a description.*
	- This data set did not include any data that will be considered sensitive in any aspect. 
16. *Any other comments?*
	- N/A

**Collection process**

1. *How was the data associated with each instance acquired? Was the data directly observable (for example, raw text, movie ratings), reported by subjects (for example, survey responses), or indirectly inferred/derived from other data (for example, part-of-speech tags, model-based guesses for age or language)? If the data was reported by subjects or indirectly inferred/derived from other data, was the data validated/verified? If so, please describe how.*
	- This data associated with each instance is through the scientifical method. 
2. *What mechanisms or procedures were used to collect the data (for example, hardware apparatuses or sensors, manual human curation, software programs, software APIs)? How were these mechanisms or procedures validated?*
	- The procedure was by examing the nature pieces of information measured by the scientists. 
3. *If the dataset is a sample from a larger set, what was the sampling strategy (for example, deterministic, probabilistic with specific sampling probabilities)?*
	- The dataset is not a sample from any existing larger set. 
4. *Who was involved in the data collection process (for example, students, crowdworkers, contractors) and how were they compensated (for example, how much were crowdworkers paid)?*
	- The data was collected by the scientists in the UK. 
5. *Over what timeframe was the data collected? Does this timeframe match the creation timeframe of the data associated with the instances (for example, recent crawl of old news articles)? If not, please describe the timeframe in which the data associated with the instances was created.*
	- The data was collected from 1984 to 2001. 
6. *Were any ethical review processes conducted (for example, by an institutional review board)? If so, please provide a description of these review processes, including the outcomes, as well as a link or other access point to any supporting documentation.*
	- There are no ethical review processes included. 
7. *Did you collect the data from the individuals in question directly, or obtain it via third parties or other sources (for example, websites)?*
	- The data was not collected by myself.
8. *Were the individuals in question notified about the data collection? If so, please describe (or show with screenshots or other information) how notice was provided, and provide a link or other access point to, or otherwise reproduce, the exact language of the notification itself.*
	- There are no individual needed to be questioned.
9. *Did the individuals in question consent to the collection and use of their data? If so, please describe (or show with screenshots or other information) how consent was requested and provided, and provide a link or other access point to, or otherwise reproduce, the exact language to which the individuals consented.*
	- There are no individual needed to be questioned.
10. *If consent was obtained, were the consenting individuals provided with a mechanism to revoke their consent in the future or for certain uses? If so, please provide a description, as well as a link or other access point to the mechanism (if appropriate).*
	- There are no individual needed to be questioned.
11. *Has an analysis of the potential impact of the dataset and its use on data subjects (for example, a data protection impact analysis) been conducted? If so, please provide a description of this analysis, including the outcomes, as well as a link or other access point to any supporting documentation.*
	- There are no analysis of potential impact of the dataset. 
12. *Any other comments?*
	- N/A

**Preprocessing/cleaning/labeling**

1. *Was any preprocessing/cleaning/labeling of the data done (for example, discretization or bucketing, tokenization, part-of-speech tagging, SIFT feature extraction, removal of instances, processing of missing values)? If so, please provide a description. If not, you may skip the remaining questions in this section.*
	- Yes, there are cleaning done by removing the Nas (missing data) from the data. 
2. *Was the "raw" data saved in addition to the preprocessed/cleaned/labeled data (for example, to support unanticipated future uses)? If so, please provide a link or other access point to the "raw" data.*
	- The 'raw' data is saved in the input folder. 
3. *Is the software that was used to preprocess/clean/label the data available? If so, please provide a link or other access point.*
	- R the programing language used, it is available to the public.
4. *Any other comments?*
	- N/A

**Uses**

1. *Has the dataset been used for any tasks already? If so, please provide a description.*
	- The data-set may be used in other tasks, but the information was not publiced. 
2. *Is there a repository that links to any or all papers or systems that use the dataset? If so, please provide a link or other access point.*
	- Code and data are available in this GitHub repository: git
3. *What (other) tasks could the dataset be used for?*
	- Any nature related task. 
4. *Is there anything about the composition of the dataset or the way it was collected and preprocessed/cleaned/labeled that might impact future uses? For example, is there anything that a dataset consumer might need to know to avoid uses that could result in unfair treatment of individuals or groups (for example, stereotyping, quality of service issues) or other risks or harms (for example, legal risks, financial harms)? If so, please provide a description. Is there anything a dataset consumer could do to mitigate these risks or harms?*
	- There are no information about the composition of the dataset.
5. *Are there tasks for which the dataset should not be used? If so, please provide a description.*
	- N/A
6. *Any other comments?*
	- N/A

**Distribution**

1. *Will the dataset be distributed to third parties outside of the entity (for example, company, institution, organization) on behalf of which the dataset was created? If so, please provide a description.*
	- The data-set will not be distributed to third parties outside of the entity.
2. *How will the dataset be distributed (for example, tarball on website, API, GitHub)? Does the dataset have a digital object identifier (DOI)?*
	- The data will be distributed on GitHub.
3. *When will the dataset be distributed?*
	- The data-set will be distributed in April 2022. 
4. *Will the dataset be distributed under a copyright or other intellectual property (IP) license, and/or under applicable terms of use (ToU)? If so, please describe this license and/ or ToU, and provide a link or other access point to, or otherwise reproduce, any relevant licensing terms or ToU, as well as any fees associated with these restrictions.*
	- The dataset will not be distributed under a copyright or other intellectual property.
5. *Have any third parties imposed IP-based or other restrictions on the data associated with the instances? If so, please describe these restrictions, and provide a link or other access point to, or otherwise reproduce, any relevant licensing terms, as well as any fees associated with these restrictions.*
	- There are no third parties imposed IP-based or other restrictions on the data associated with the instances.
6. *Do any export controls or other regulatory restrictions apply to the dataset or to individual instances? If so, please describe these restrictions, and provide a link or other access point to, or otherwise reproduce, any supporting documentation.*
	- There are no export controls or other regulatory restrictions apply to the dataset or to individual instances.
7. *Any other comments?*
	- N/A

**Maintenance**

1. *Who will be supporting/hosting/maintaining the dataset?*
	- Cheng Chen
2. *How can the owner/curator/manager of the dataset be contacted (for example, email address)?*
	- By E-mail at "Cheng.chen@mail.utoronto.ca"
3. *Is there an erratum? If so, please provide a link or other access point.*
	- There are no erratum
4. *Will the dataset be updated (for example, to correct labeling errors, add new instances, delete instances)? If so, please describe how often, by whom, and how updates will be communicated to dataset consumers (for example, mailing list, GitHub)?*
	- There are no plane to update the data-set. It is hard to get data from UK.
5. *If the dataset relates to people, are there applicable limits on the retention of the data associated with the instances (for example, were the individuals in question told that their data would be retained for a fixed period of time and then deleted)? If so, please describe these limits and explain how they will be enforced.*
	- There are no pplicable limits on the retention of the data associated with the instances.
6. *Will older versions of the dataset continue to be supported/hosted/maintained? If so, please describe how. If not, please describe how its obsolescence will be communicated to dataset consumers.*
	- Older version will not be hosted. 
7. *If others want to extend/augment/build on/contribute to the dataset, is there a mechanism for them to do so? If so, please provide a description. Will these contributions be validated/verified? If so, please describe how. If not, why not? Is there a process for communicating/distributing these contributions to dataset consumers? If so, please provide a description.*
	- The repository can be extend/augment/build on/contribute to. I (the writer of this report) will not be responsible for any responsivlity. 
8. *Any other comments?*
	- N/A

\newpage

# References